%% Master CV - Gustavo Pernas
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs.
%%
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black, which
% looks inconsistent with the rest of the blue accent scheme.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Gustavo Pernas - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}
\usepackage{needspace}

% personal data
\name{Gustavo}{Pernas}
\address{Dublin, Ireland}{}{}
\phone[mobile]{+353 86 041 3984}
\email{guspernas@gmail.com}
\extrainfo{\href{https://www.linkedin.com/in/gustavopernas}{LinkedIn}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{Operations and service delivery leader with 10+ years across B2B technology platforms and 5+ years leading regional client services, support and customer success organisations. Led 50+ specialists across 34 markets and 10 languages, covering internal and outsourced (BPO) delivery. Delivered 2.5x productivity growth, +40\% CSAT, 84\% faster first response and 55\% faster resolution through service redesign, live chat, workflow automation, AI-enabled optimisation and KPI governance. Combines performance accountability, people development and cross-functional leadership across EMEA and LATAM.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Client Services \& Customer Success}: Service delivery, customer success operations, escalation management, CSAT / SLA / FRT / TTR governance, voice of customer.

\item \textbf{Operations \& Transformation}: Operating-model design, process improvement, workflow optimisation, AI-enabled automation, programme management, change management (ADKAR, Agile).

\item \textbf{Vendor \& BPO Management}: Multi-vendor performance management, activation programmes, SOPs, weekly business reviews, quality assurance.

\item \textbf{Commercial \& Sales Leadership}: Revenue growth, account and partner management, consultative sales, cross-regional sales programmes.

\item \textbf{People \& Stakeholders}: Hiring, coaching, team development, cross-functional leadership, executive stakeholder management.

\item \textbf{Platforms \& Analytics}: Salesforce, CRM and ticketing platforms, knowledge management systems, SQL, Tableau, data analytics, billing systems.

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

% --- TikTok: MPO Lead ---
\needspace{5\baselineskip}
\item{\cventry{2024--2025}{Regional MPO Lead, Solutions Engineering, EMEA}{TikTok}{Dublin, Ireland}{}{\vspace{1pt}
\begin{itemize}
    \item Led operational transformation of a 40+ Technical Support Engineer organisation across EMEA and LATAM (follow-the-sun), delivering 2.5x productivity growth through AI-enabled process optimisation and cross-functional collaboration.
    \item Partnered with Product teams to scale workflow improvements, improving the consistency and efficiency of post-sales delivery.
    \item Implemented a Refund Abuse Prevention framework, reducing abuse volume by 48\% with Legal, Fraud and Ad Exchange teams.
\end{itemize}}}

\vspace{3pt}

% --- TikTok: Head of Client Services ---
\needspace{5\baselineskip}
\item{\cventry{2021--2024}{Head of Client Services, EMEA}{TikTok}{Dublin, Ireland}{}{\vspace{1pt}
\begin{itemize}
    \item Led 50+ support specialists across 34 markets and 10 languages, owning CSAT, SLA attainment, First Response Time, First Touch Resolution, Time to Resolution, quality and escalation performance across internal and vendor-supported delivery.
    \item Launched Concierge Support across EMEA and LATAM, cutting First Response Time by 84\% and Time to Resolution by 55\%.
    \item Created hybrid Live Chat support for EMEA and Brazil, improving CSAT by 40\% and reducing escalations by 28\%.
    \item Redesigned global process workflows with KPI tracking and executive dashboards, accelerating decision-making by 20\%; reduced suspension-appeal escalations from 81\% to below 60\%.
    \item Served seven months as Interim Global Head of Client Services, aligning regional teams on common standards, workflows and performance expectations.
\end{itemize}}}

\vspace{3pt}

% --- TikTok: Vendor Manager Lead ---
\needspace{5\baselineskip}
\item{\cventry{2020--2022}{Regional Vendor Manager Lead, EMEA (concurrent)}{TikTok}{Dublin, Ireland}{}{\vspace{1pt}
\begin{itemize}
    \item Managed performance across four BPO partners; introduced an Activation Program with KPI dashboards and weekly reviews, increasing advertiser activation by 30\%.
    \item Launched sales programmes through cross-regional partnerships, increasing vendor-led revenue by 20\%.
\end{itemize}}}

\vspace{3pt}

% --- Pinterest ---
\needspace{5\baselineskip}
\item{\cventry{2019--2020}{Partnerships}{Pinterest}{Dublin, Ireland}{}{\vspace{1pt}
\begin{itemize}
    \item Built customer success programmes for key partners using audience insights and performance data, achieving partner retention above 85\%.
    \item Delivered process improvements that doubled partner engagement.
\end{itemize}}}

\vspace{3pt}

% --- Meta ---
\needspace{5\baselineskip}
\item{\cventry{2014--2019}{Partner \& Project Manager / Senior Partner Manager}{Meta (Global Business Group)}{Dublin, Ireland}{}{\vspace{1pt}
\begin{itemize}
    \item Managed cross-functional projects with Product and Engineering to build regional sports ad solutions; served as Interim Sales Leader.
    \item Led revenue-growth initiatives across Spanish and Portuguese SMB markets in e-commerce and fashion, improving adoption and campaign performance.
\end{itemize}}}

\vspace{3pt}

% --- Google / Trabe ---
\needspace{5\baselineskip}
\item{\cventry{2005--2013}{Account Manager \& Quality Lead / Business Development Manager}{Google (via TTEC), Trabe Gesti\'on}{Dublin \& Lugo}{}{\vspace{1pt}
\begin{itemize}
    \item Google: managed advertiser support and quality for AdWords/Shopping across UK and Spanish-language markets; coached account managers as Quality Lead.
    \item Trabe: led a six-person sales team to 200\% sales growth in 14 months through process improvement and consultative B2B sales to banking clients.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{2010--2011}{Master of Business Administration (MBA)}{Hult International Business School}{}{}{}}

\vspace{3pt}

\item{\cventry{1996--2001}{Bachelor of Business Administration (BBA)}{University of Santiago de Compostela}{Spain}{}{}}

\end{itemize}

% ============================================================
%     PROFESSIONAL DEVELOPMENT / CERTIFICATIONS
% ============================================================

\section{Professional Development}
\vspace{1pt}
\begin{itemize}
\item Professional Diploma in Advanced Artificial Intelligence (Distinction), UCD Professional Academy (2026).
\item Professional Diploma in Operations Strategy, Hult International Business School (2026).
\item Diploma in Change Management, Operations Management and Supervision, UCD Professional Academy (2023).
\item Google Search Advertising Advanced; Google Advertising Fundamentals (2013).
\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Spanish (native), English (fluent), Portuguese (professional), French (basic).
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
